---
title: "Fear & Greed Index"
output: html_document
date: "2024-01-18"
---
Index: <https://www.cnn.com/markets/fear-and-greed#fng-faq>
```{r setup, include=FALSE}
require("quantmod");require("dplyr");require("RQuantLib");require("scales");require("plotly")
```

## 1. MARKET MOMENTUM

S&P 500 and its 125-day moving average
```{r marketMomentum, echo=FALSE}
# Market Momentum - S&P 500
market_momo = getSymbols("^GSPC",from="1970-01-01",auto.assign = FALSE)
# keep business days only
market_momo = market_momo[isBusinessDay(calendar = "UnitedStates/NYSE",dates = index(market_momo)),]
# add 150-day MA
market_momo$ma150 = SMA(Cl(market_momo), n = 150)
# difference between close and moving avg
market_momo$sprd = Cl(market_momo)/market_momo$ma150-1
# remove NAs
market_momo = na.omit(market_momo)
# rank spread
market_momo$rank <- rank(as.numeric(market_momo$sprd))/nrow(market_momo)
```

## 2. STOCK PRICE STRENGTH
Get 52-week Hi/Lo from FinViz
```{r wk52, echo=FALSE}
# list FinViz Files
FILES = list.files("/Volumes/6TB/FinViz-Stats",pattern = "20+",full.names = T)
# for each file extract the Net 52-week's
wk52 = lapply(as.list(FILES), function(x){
  # read in file
  tmp = readRDS(x)
  # 52-Week Highs
  wk52_hi = subset(tmp,tmp$Price == tmp$`52W High $`)
  wk52_lo = subset(tmp,tmp$Price == tmp$`52W Low $`)
  # create xts
  xts(round(nrow(wk52_hi)/nrow(wk52_lo),4), order.by = as.Date(tmp$Date[1]))
})
# rowbind all
wk52 = do.call(rbind,wk52)
# clean data
wk52 = make.index.unique(wk52, drop = T)
wk52[is.nan(wk52)] <- 0
wk52[is.infinite(wk52)] <- 0
# rename column
colnames(wk52) = "net52wk"
# rank
wk52$rank <- rank(as.numeric(wk52$net52wk))/nrow(wk52)
#wk52 <- readRDS('wk52.rds')
```

## 3. STOCK PRICE BREADTH
Measure of volume for stocks that are up vs the down
```{r stockPrcBreadth, echo=FALSE}
# list FinViz Files
FILES = list.files("/Volumes/6TB/FinViz-Stats",pattern = "20+",full.names = T)
# for each file extract the Net Volume
breadth = lapply(as.list(FILES), function(x){
  # read in file
  tmp = readRDS(x)
  # gather by volume
  tot_vol = tmp %>% reframe(up_vol = sum(Volume[Change >= 0],na.rm = T),
                        dn_vol = sum(Volume[Change < 0],na.rm = T)
  )
  # create xts
  xts(round(tot_vol$up_vol/tot_vol$dn_vol,4), order.by = as.Date(tmp$Date[1]))
})
# rowbind all
breadth = do.call(rbind,breadth)
# clean data
breadth = make.index.unique(breadth, drop = T)
breadth[is.nan(breadth)] <- 0
breadth[is.infinite(breadth)] <- 0
# rename column
colnames(breadth) = "breadth"
# rank
breadth$rank <- rank(as.numeric(breadth$breadth))/nrow(breadth)
#breadth <- readRDS("breadth.rds")
```

## 4. PUT AND CALL OPTIONS

Historical Put/Call Ratio
```{r putCall, echo=FALSE}
# list computed option stats
FILES = list.files("/Volumes/6TB/CBOE/market_stats",full.names = T)
# for each file extract the Put/Call Ratio
putCall = lapply(as.list(FILES), function(x){
  # read in file
  tmp = readRDS(x)
  # gather by volume
  pc = subset(tmp,tmp$flag == "P")$totalVolume/subset(tmp,tmp$flag == "C")$totalVolume
  # create xts
  xts(round(pc[1],4), order.by = as.Date(tmp$Date[1]))
})
# rowbind all
putCall = do.call(rbind,putCall)
# clean data
putCall = make.index.unique(putCall, drop = T)
putCall[is.nan(putCall)] <- 0
putCall[is.infinite(putCall)] <- 0
# rename column
colnames(putCall) = "putCall"
# 5-Day Moving average
putCall$ma5 <- SMA(putCall, n = 5)
# omit NAs
putCall <- na.omit(putCall)
# rank
putCall$rank <- rank(as.numeric(putCall$ma5))/nrow(putCall)
#putCall <- readRDS("putCall.rds")
```


## 5. MARKET VOLATILITY

Using VIX and its 50-day moving average
```{r vix, echo=FALSE}
# list computed option stats
VIX = getSymbols("^VIX", from="1970-01-01",auto.assign = FALSE) %>% suppressWarnings() %>% suppressMessages()
# keep business days only
VIX = VIX[isBusinessDay(calendar = "UnitedStates/NYSE",dates = index(VIX)),]
# add 50-day MA
VIX$ma50 = SMA(Cl(VIX), n = 50)
# difference between close and moving avg
VIX$sprd = Cl(VIX)/VIX$ma50-1
# remove NAs
VIX = na.omit(VIX)
# rank spread
VIX$rank <- rank(as.numeric(VIX$sprd))/nrow(VIX)
```


## 6. SAFE HAVEN DEMAND

Difference in 20-day stock and bond returns
```{r safeHaven, echo=FALSE}
#  Get Market returns
MARKET = getSymbols("^GSPC", from="1970-01-01",auto.assign = FALSE) %>% suppressWarnings() %>% suppressMessages()
# keep business days only
MARKET = MARKET[isBusinessDay(calendar = "UnitedStates/NYSE",dates = index(MARKET)),]
# calculate returns
MARKET = ROC(Cl(MARKET))
# get bond returns - 1yr
getSymbols.FRED(Symbols = "DGS1",env = .GlobalEnv)
# convert to daily returns
BONDS = DGS1/100/365
if(index(tail(BONDS,1)) != index(tail(MARKET,1))){
  BONDS = na.locf(rbind(BONDS, xts(NA, order.by = index(tail(MARKET,1)))))
}
# MARKET VS BONDS
NET = na.omit(merge(MARKET,BONDS))
NET = NET[,1]-NET[,2]
# smooth out using a 20-day MA
NET$ma20 = SMA(NET[,1], n = 20)
# rank
NET$rank <- rank(as.numeric(NET[,1]))/nrow(NET)
```

## 7. JUNK BOND DEMAND

Yield spread: junk bonds vs. investment grade
```{r junkBonds, echo=FALSE}
# get junk bond yields - https://fred.stlouisfed.org/series/BAMLH0A0HYM2EY
getSymbols.FRED(Symbols = "BAMLH0A0HYM2EY",env = .GlobalEnv)
# convert to daily returns
JUNK_BONDS = BAMLH0A0HYM2EY/100/365
if(index(tail(JUNK_BONDS,1)) != index(tail(MARKET,1))){
  JUNK_BONDS = na.locf(rbind(JUNK_BONDS, xts(NA, order.by = index(tail(MARKET,1)))))
}
# get investment grade yields - https://fred.stlouisfed.org/series/AAA
getSymbols.FRED(Symbols = "AAA",env = .GlobalEnv)
# convert to daily returns
INV_BONDS = AAA/100/365
if(index(tail(INV_BONDS,1)) != index(tail(MARKET,1))){
  INV_BONDS = na.locf(rbind(INV_BONDS, xts(NA, order.by = index(tail(MARKET,1)))))
}
# NET YIELD
NET_YIELD = na.omit(merge(JUNK_BONDS,INV_BONDS))
NET_YIELD = NET_YIELD[,1]-NET_YIELD[,2]
# rank
NET_YIELD$rank <- rank(as.numeric(NET_YIELD[,1]))/nrow(NET_YIELD)
```

## RANK ALL
We will rank the last observation 
```{r rankings, echo=FALSE}
# 1. MARKET MOMENTUM RANK
f1 <- as.numeric(tail(market_momo$rank,1))
# 2. STOCK PRICE STRENGTH RANK
f2 <- as.numeric(tail(wk52$rank,1))
# 3. STOCK PRICE BREADTH RANK
f3 <- as.numeric(tail(breadth$rank,1))
# 4. PUT AND CALL OPTIONS RANK
f4 <- as.numeric(tail(putCall$rank,1))
# 5. MARKET VOLATILITY RANK
f5 <- as.numeric(tail(VIX$rank,1))
# 6. SAFE HAVEN DEMAND RANK 
f6 <- as.numeric(tail(NET$rank,1))
# 7. JUNK BOND DEMAND RANK
f7 <- as.numeric(tail(NET_YIELD$rank,1))
# MEAN READING 
AVG <- mean(c(f1,f2,f3,f4,f5,f6,f7))
# print results
cat("\n",sprintf("%-55s", '       Category               | Latest '),
    "\n",sprintf("%-55s", paste0("1. MARKET MOMENTUM RANK       | ", scales::percent(f1,accuracy = 0.01))),
    "\n",sprintf("%-55s", paste0("2. STOCK PRICE STRENGTH RANK  | ", scales::percent(f2,accuracy = 0.01))),
    "\n",sprintf("%-55s", paste0("3. STOCK PRICE BREADTH RANK   | ", scales::percent(f3,accuracy = 0.01))),
    "\n",sprintf("%-55s", paste0("4. PUT AND CALL OPTIONS RANK  | ", scales::percent(f4,accuracy = 0.01))),
    "\n",sprintf("%-55s", paste0("5. MARKET VOLATILITY RANK     | ", scales::percent(f5,accuracy = 0.01))),
    "\n",sprintf("%-55s", paste0("6. SAFE HAVEN DEMAND RANK     | ", scales::percent(f6,accuracy = 0.01))),
    "\n",sprintf("%-55s", paste0("7. JUNK BOND DEMAND RANK      | ", scales::percent(f7,accuracy = 0.01))),
    "\n",sprintf("%-55s", paste0("OVERALL RANK................... ", scales::percent(AVG,accuracy = 0.01)))
)


```
## RANK ALL - PREVIOUS READING
We will rank the last observation 
```{r rankings, echo=FALSE}
# 1. MARKET MOMENTUM RANK
p1 <- as.numeric(tail(market_momo$rank,2))[1]
# 2. STOCK PRICE STRENGTH RANK
p2 <- as.numeric(tail(wk52$rank,2))[1]
# 3. STOCK PRICE BREADTH RANK
p3 <- as.numeric(tail(breadth$rank,2))[1]
# 4. PUT AND CALL OPTIONS RANK
p4 <- as.numeric(tail(putCall$rank,2))[1]
# 5. MARKET VOLATILITY RANK
p5 <- as.numeric(tail(VIX$rank,2))[1]
# 6. SAFE HAVEN DEMAND RANK 
p6 <- as.numeric(tail(NET$rank,2))[1]
# 7. JUNK BOND DEMAND RANK
p7 <- as.numeric(tail(NET_YIELD$rank,2))[1]
# MEDIAN READING - (TO EXCLUDE OUTLIERS)
pAVG <- mean(c(p1,p2,p3,p4,p5,p6,p7))
# print results
cat("\n",sprintf("%-55s", '       Category               | Latest '),
    "\n",sprintf("%-55s", paste0("1. MARKET MOMENTUM RANK       | ", scales::percent(p1,accuracy = 0.01))),
    "\n",sprintf("%-55s", paste0("2. STOCK PRICE STRENGTH RANK  | ", scales::percent(p2,accuracy = 0.01))),
    "\n",sprintf("%-55s", paste0("3. STOCK PRICE BREADTH RANK   | ", scales::percent(p3,accuracy = 0.01))),
    "\n",sprintf("%-55s", paste0("4. PUT AND CALL OPTIONS RANK  | ", scales::percent(p4,accuracy = 0.01))),
    "\n",sprintf("%-55s", paste0("5. MARKET VOLATILITY RANK     | ", scales::percent(p5,accuracy = 0.01))),
    "\n",sprintf("%-55s", paste0("6. SAFE HAVEN DEMAND RANK     | ", scales::percent(p6,accuracy = 0.01))),
    "\n",sprintf("%-55s", paste0("7. JUNK BOND DEMAND RANK      | ", scales::percent(p7,accuracy = 0.01))),
    "\n",sprintf("%-55s", paste0("OVERALL RANK................... ", scales::percent(pAVG,accuracy = 0.01)))
)


```

## Create Market Gauge

```{r marketGauge, echo=FALSE}

fig <- plot_ly(
  domain = list(x = c(0, 1), y = c(0, 1)),
  value = round(AVG,4)*100,
  title = list(text = "Fear & Greed Index"),
  type = "indicator",
  mode = "gauge+number+delta",
  delta = list(reference = round(pAVG,4)*100),
  gauge = list(
    axis =list(range = list(NULL, 100),tickvals = seq(0,100,5)),
    bar = list(color = "black"),
    steps = list(
      list(range = c(0, 24.99), color = "#f44336"),
      list(range = c(25, 44.99), color = "#ff930f"),
      list(range = c(45, 54.99), color = "#ffcb2c"),
      list(range = c(55, 74.99), color = "#53adff"),
      list(range = c(75, 100), color = "#8fce00")),
    threshold = list(
      line = list(color = "red", width = 4),
      thickness = 0.75,
      value = round(AVG,4)*100))) 

fig <- fig %>%
  layout(margin = list(l=20,r=30)) %>%
  add_annotations(text="Extreme Fear", x=0.17, y=0.35, showarrow=FALSE) %>% 
  add_annotations(text="Fear", x=0.35, y=0.62, showarrow=FALSE) %>%
  add_annotations(text="Neutral", x=0.50, y=0.71, showarrow=FALSE) %>%
  add_annotations(text="Greed", x=0.68, y=0.62, showarrow=FALSE) %>%
  add_annotations(text="Extreme Greed", x=0.83, y=0.35, showarrow=FALSE)

fig

```