---
title: "Get ETF Constituents From SPDR, Invesco, iShares"
output:
  html_document:
    df_print: paged
geometry: margin=1cm
date: '`r format(Sys.Date(), "%A, %B %d, %Y")`'
editor_options: 
  markdown: 
    wrap: sentence
---

```{=html}
<style>
body {
    position: absolute;
    left: 0px;}
</style>
```
```{r setup, include=FALSE}
setwd("/Volumes/6TB/R")
# get constituent data
suppressPackageStartupMessages(require("readxl"))
suppressPackageStartupMessages(require("data.table"))
suppressPackageStartupMessages(require("dplyr"))
suppressPackageStartupMessages(require("quantmod"))
```


### SPDR ETFs
SPDR provides constituent data for all products. We can download all as a batch but are downloaded as .xlsx files. We can specify a location on where to save them and then read them into R. 
```{r spdr, echo=FALSE,warning=FALSE}

# download all daily holdings
getSPDR = function(PATH,dl_Date){
  # url to zip file
  URL = paste0("https://www.ssga.com/library-content/products/fund-data/etfs/us/us_spdrallholdings.zip")
  # download the zipped file
  download.file(url = URL, quiet = TRUE,destfile = paste0(getwd(),"/SPDR.zip"))
  # unzip the file to a different location 
  unzip(paste0(getwd(),"/SPDR.zip"),exdir = paste0(PATH,"SPDR_",format(dl_Date,"%Y%m%d")))
}
# read in XLSX files
readSPDR = function(PATH,dl_Date,ticker){
  # where is the file located
  FILE = paste0(PATH,"SPDR_",format(dl_Date,"%Y%m%d"),"/","holdings-daily-us-en-",tolower(ticker),".xlsx")
  # read in file
  tbl <- readxl::read_xlsx(FILE) %>% suppressMessages() %>% suppressWarnings()
  # removes unused rows
  tbl <- na.omit(tbl)
  # reassign column names
  colnames(tbl) <- tbl[1,]
  # drop first row
  tbl <-  tbl[-1,]
  # return table
  tbl
}
# read in ALL
readAllSPDR = function(PATH){
  # list all folders
  FOLDERS <- list.files(PATH)
  # list all file paths
  FILES = do.call(c,lapply(as.list(FOLDERS), function(x){
    list.files(paste0(PATH,x),full.names = TRUE)
  }))
  # for each of the files combine into a single variable
  ETFS = lapply(as.list(FILES), function(x){
    # get ETF name
    getName <- str_split(x,"/",simplify = TRUE)
    getName <- as.character(getName[,ncol(getName)])
    getName <- gsub("holdings-daily-us-en-","",getName)
    getName <- gsub(".xlsx","",getName)
    getName <- toupper(getName)
    # read in file
    tbl <- read_xlsx(x) %>% suppressMessages() %>% suppressWarnings()
    # removes unused rows
    tbl <- na.omit(tbl)
    # reassign column names
    colnames(tbl) <- tbl[1,]
    # drop first row
    tbl <-  tbl[-1,]
    # add ETF name
    tbl$ETF <- getName
    # return table
    tbl
  })
  # rbind all tables 
  ETFS <- rbindlist(ETFS,use.names = TRUE,fill = TRUE)
  # set columns to numeric
  setDT(ETFS)[, c(4:7) := lapply (.SD, function(x) round(as.numeric(x),4)), .SDcols=c(4:7)] %>% suppressWarnings() %>% suppressMessages()
  # change Weight to proper format
  ETFS$Weight <- as.numeric(ETFS$Weight)/100
  # return table
  ETFS
}


```

## Test SPDR
Specify a path in your computer where to 'unzip' the files to. R will use this location to read in the .xlsx files.
```{r testSPDR, echo=FALSE,warning=FALSE}
# downloads as .xlsx file - use require("readxl") to read them into RStudio
PATH = paste0("/Volumes/6TB/constituents/SPDR/")
dl_Date = Sys.Date()
# get all SPDR ETF data
getSPDR(PATH,dl_Date = Sys.Date())

# read in individual ETFS
SPY <- readSPDR(PATH,ticker="SPY",dl_Date = Sys.Date())
DIA <- readSPDR(PATH,ticker="DIA",dl_Date = Sys.Date())
BIL <- readSPDR(PATH,ticker="BIL",dl_Date = Sys.Date())
XLK <- readSPDR(PATH,ticker="XLK",dl_Date = Sys.Date())
# read in all ETFS - takes some time to run!
#all_etfs = readAllSPDR(PATH)
all_etfs <- readRDS("all_etfs.rds")
# subset stock ETFS only (exclude bonds/bill etfs)
stk_etfs = subset(all_etfs,!is.na(all_etfs$Ticker))
stk_etfs = stk_etfs[,c("Name", "Weight","Local Currency", "ETF","Ticker", "Shares Held")]
colnames(stk_etfs) <- c("name","weight","currency","etf","ticker","sharesHeld")
stk_etfs <- as.data.frame(stk_etfs)
# replace "-" tickers with CASH
stk_etfs$ticker <- gsub("-","CASH",stk_etfs$ticker)
# we can use the table to aggregate by symbol and see how many shares have been bought
stk_etfs$sharesHeld <- as.numeric(stk_etfs$sharesHeld)
totalShares <- stk_etfs %>% group_by(ticker) %>% summarise(totalShares = sum(sharesHeld,na.rm = TRUE),
                                                           etfCount = n(),
                                                           avgWt = mean(weight,na.rm = TRUE),
                                                           sumWt = sum(weight,na.rm = TRUE))
totalShares<- totalShares[order(totalShares$sumWt,decreasing = TRUE),]
View(subset(stk_etfs,stk_etfs$ticker == "NVDA"))

```


### Invesco ETFs

Invesco provides a list of products which we can download directly into R. We can also read them into R by assigning a ticker symbol into the getInvescoETF function.
```{r invesco, echo=FALSE,warning=FALSE}

# INVESCO
getInvescoProducts= function(){
  URL = "https://www.invesco.com/us/financial-products/etfs/performance/prices/main/performance/0?audienceType=Investor&action=download"
  tbl <- readLines(URL)
  # filter out the repeating, and wonky headers
  tbl_2 <- grep("Node Name,RTC_date", tbl, invert=TRUE, value=TRUE)
  # turn that vector into a text connection for read.csv
  tbl_3 <- read.csv(textConnection(paste0(tbl_2, collapse="\n")),header=FALSE, stringsAsFactors=FALSE)
  # skip over NA lines
  tbl <- tbl_3[which(tbl_3$V1 == "Name"):nrow(tbl_3),]
  # change column names
  colnames(tbl) <- tbl[1,]
  # remove 1st row
  tbl <- tbl[-1,]
  # return tbl
  tbl
}
# get constituents for invesco ets
getInvescoETF = function(ticker){
  Sys.sleep(5)
  # create url
  url = paste0("https://www.invesco.com/us/financial-products/etfs/holdings/main/holdings/0?audienceType=Investor&action=download&ticker=",
               ticker)
  # read in data
  df <- read.csv2(url,header =TRUE,sep = ",")
  # format columns
  df$MarketValue <- as.numeric(gsub("\\,","",df$MarketValue))
  df$Weight <- as.numeric(df$Weight)/100
  df$Shares.Par.Value <- as.numeric(gsub("\\,","",df$Shares.Par.Value))
  # return data
  df
}

```

## Test Invesco
Get Product list and also read in a couple of their ETFs.
```{r testInvesco, echo=FALSE,warning=FALSE}
# get product list
invProd <- getInvescoProducts()
# test function
QQQ  <- getInvescoETF("QQQ")   # Invesco QQQ
QQQS <- getInvescoETF("QQQS")  # Invesco NASDAQ Future Gen 200 ETF
PSP  <- getInvescoETF("PSP")   # Invesco Global Listed Private Equity ETF
ADRE <- getInvescoETF("ADRE")  # Invesco BLDRS Emerging Markets 50 ADR Index Fund 

```


### iShares ETFs

iShares is a bit picky with their links. Each link has a product "ID" along with the full name of the ETF embeded. We can try parsing the urls in the future but we will just display a couple with manual assigning.
```{r ishares, echo=FALSE,warning=FALSE}

getiSharesETF = function(){
  URL = "https://www.ishares.com/us/products/239710/ishares-russell-2000-etf/1467271812596.ajax?fileType=csv&fileName=IWM_holdings&dataType=fund"
  # URL = "https://www.ishares.com/us/products/239454/ishares-20-year-treasury-bond-etf/1467271812596.ajax?fileType=csv&fileName=TLT_holdings&dataType=fund"
  # URL = "https://www.ishares.com/us/products/239763/ishares-core-sp-midcap-etf/1467271812596.ajax?fileType=csv&fileName=IJH_holdings&dataType=fund
  # URL = "https://www.ishares.com/us/products/244049/ishares-core-msci-eafe-etf/1467271812596.ajax?fileType=csv&fileName=IEFA_holdings&dataType=fund"
  ETF <- read.csv(URL,skip = 9,header = TRUE)
  ETF
}

```

## Test iShares
Get IWM ETF constituents.
```{r testIShares, echo=FALSE,warning=FALSE}
# test function
IWM <- getiSharesETF()

```