---
title: "Historical Risk Premiums"
output:
  html_document:
    df_print: paged
geometry: margin=1cm
date: '`r format(Sys.Date()-1, "%A, %B %d, %Y")`'
---

```{=html}
<style>
body {
    position: absolute;
    left: 0px;}
</style>
```
```{r setup, include=FALSE}
#setwd("/Volumes/6TB/R")
suppressPackageStartupMessages(require("quantmod"))
suppressPackageStartupMessages(require("lubridate"))
suppressPackageStartupMessages(require("PerformanceAnalytics"))
#source("/Volumes/6TB/R/getFinHub.R")
# tinytex::install_tinytex()
DATE <- Sys.Date()-1
daytoday <- format(DATE,"%Y%m%d")
```

## Get Stock Data

We will start by getting stock OHLCV data from FinHub

```{r getData}
# assign a benchmark
bm = "QQQ"
# assign stocks
# Qs = readRDS("/Volumes/6TB/constituents/invesco/20230626.rds")
# Qs = subset(Qs,Qs$Fund.Ticker=="QQQ")
stks = c("MSFT", "AAPL", "AMZN", "NVDA", "META", "TSLA", "GOOGL", "GOOG", 
         "AVGO", "PEP", "COST", "ADBE", "CSCO", "NFLX", "AMD", "CMCSA", 
         "TMUS", "TXN", "INTC", "HON", "QCOM", "INTU", "AMGN", "AMAT", 
         "ISRG", "SBUX", "MDLZ", "BKNG", "GILD", "ADI", "VRTX", "ADP", 
         "REGN", "LRCX", "PANW", "PYPL", "MU", "CSX", "ATVI", "SNPS", 
         "KLAC", "ASML", "CDNS", "MNST", "MELI", "ORLY", "FTNT", "MAR", 
         "ABNB", "CHTR", "NXPI", "MRVL", "CTAS", "DXCM", "MRNA", "LULU", 
         "WDAY", "MCHP", "KDP", "KHC", "AEP", "ADSK", "CPRT", "PDD", "AZN", 
         "PCAR", "BIIB", "EXC", "IDXX", "PAYX", "ON", "SGEN", "ROST", 
         "ODFL", "CSGP", "GEHC", "XEL", "EA", "FAST", "GFS", "VRSK", "CRWD", 
         "CTSH", "DLTR", "BKR", "ILMN", "CEG", "WBD", "DDOG", "ANSS", 
         "WBA", "ALGN", "TEAM", "EBAY", "FANG", "ENPH", "ZS", "ZM", "JD", 
         "SIRI", "LCID")

ticker_vec = c(bm,stks)
# get stock data for 5 years
ALL <- do.call(merge,lapply(as.list(c(ticker_vec)), function(x){
  #cat("\n",x)
  if((which(x == ticker_vec) %% 30) == 0){Sys.sleep(3)}
  tmp <- try(getStkCandlesFH(stk=x,res="D",from=Sys.Date()-lubridate::years(5), to = Sys.Date(),apiKey = pw$apiKey), silent = TRUE)
  if(inherits(tmp,'try-error')){
    tmp = Cl(getSymbols(Symbols = x,from=Sys.Date()-lubridate::years(5), auto.assign = FALSE))
    colnames(tmp) = gsub(".Close","",names(tmp))
  }else{
  # convert to xts
  tmp = xts(tmp$close,order.by = as.Date(tmp$timeStamp));colnames(tmp)<-c(x)
    }
  # return xts
  tmp
  }))

# get daily returns for all stocks
RETS <- ROC(ALL)

# for the risk free rate we will use the 1 month rate and convert to daily
getSymbols.FRED(Symbols = "DGS1MO", env = .GlobalEnv)
# na fill
DGS1MO = na.locf(DGS1MO)
# convert to daily rate
DGS1MO = DGS1MO/100/360
# subset interest rate to match XTS
DGS1MO = DGS1MO[index(ALL)]
```

## Calculate risk premiums

We will use `PerformanceAnalytics::CAPM.RiskPremium()`

The CAPM Risk Premium on an investment is the measure of how much the asset's performance differs from the risk free rate. Negative Risk Premium generally indicates that the investment is a bad investment, and the money should be allocated to the risk free asset or to a different asset with a higher risk premium.

```{r riskPremiums, echo=FALSE}

tbl_rets = merge(RETS,DGS1MO)
tbl_rets[is.na(tbl_rets)] <- 0
# compute risk premiums for all stocks
risk_prem = apply.monthly(RETS, FUN = function(x) PerformanceAnalytics::CAPM.RiskPremium(Ra=x, Rf=tbl_rets$DGS1MO))

```

## Assign Stock + Plot Risk-Premium

```{r assignSTK, echo=FALSE, fig.keep='last', warning=FALSE}

stk = "META"
tbl_plot = na.locf(merge(tbl_rets[,stk], risk_prem[,stk])) 
colnames(tbl_plot) = c("stk","risk_prem")
chartSeries(cumsum(tbl_plot$stk), name=stk)
addTA(tbl_plot$risk_prem, col="red")
```


## Add Trading signals

We will add trading signals for long/short entries:

Rules: 

1. Long as long as the risk premium is positive 

2. Short as long as the risk premium is negative + Buy 1-month treasury

```{r trade, echo=FALSE, warning=FALSE, fig.keep='last'}
# rebalancing occurs the last trading day of each month
trade_tbl <- tbl_plot
# create the trading signals
trade_tbl$sig = ifelse(trade_tbl$risk_prem < 0, -1, 1) 
# add risk free-rate
trade_tbl$Rf = tbl_rets$DGS1MO

# add returns
# Long-Stock Returns:
trade_tbl$long_return_stk = ifelse(trade_tbl$sig == 1, trade_tbl$stk*trade_tbl$sig,0)
# Short-Stock Returns:
trade_tbl$short_return_stk = ifelse(trade_tbl$sig == -1, trade_tbl$stk*trade_tbl$sig,0)
# Long 1-Month Treasury - if short
trade_tbl$long_return_bill <- 0
# endpoints
eps = endpoints(trade_tbl,on="months")
# if the signal is short add bill return - bill is 28 days for 1 month
ifelse(trade_tbl[eps,"sig"]==-1, trade_tbl[eps,"long_return_bill"]<- as.numeric(trade_tbl[eps,"Rf"])*28,0)
# add return of long-stock + T-Bill (no shorting)
trade_tbl$long_stk_long_bill = trade_tbl$long_return_stk + trade_tbl$long_return_bill 
# 50% allocations - 50% short & 50% t-bills
trade_tbl$short_return_stk <- trade_tbl$short_return_stk*0.50
trade_tbl$long_return_bill <- trade_tbl$long_return_bill*0.50
# add total return
trade_tbl$total_return = as.numeric(trade_tbl$long_return_stk+trade_tbl$short_return_stk+trade_tbl$long_return_bill)
# plot returns
# charts.PerformanceSummary(merge(trade_tbl$stk,trade_tbl[,c("long_return_stk","short_return_stk",
#                                                            "long_return_bill","total_return","long_stk_long_bill")]),
#                           geometric = FALSE, cex.legend=1.25,main = paste0("Risk-Premium Trading: ",stk))
chart.CumReturns(merge(trade_tbl$stk,trade_tbl[,c("long_return_stk","short_return_stk",
                                                           "long_return_bill","total_return","long_stk_long_bill")]),legend.loc = "topleft",
                          geometric = FALSE,main = paste0("Risk-Premium Trading: ",stk))
```