---
title: "Implied Volatility Spikes"
output: html_document
date: "2024-01-25"
---
The purpose of this script is to find the average number of days (before earnings) & finding out when implied volatility spikes.
```{r setup, include=FALSE}
require("quantmod");require("dplyr");require("RQuantLib");require("lubridate");require("rvest")
# source option db
#source("getOptionSymbolsDB.R")
# assignment
sym = "PLTR"
```

## Get earnings dates

We will get the historical earnings release dates
```{r getEPS, echo=FALSE}
getEPS = function(ticker, before){
  # build url
  URL <- paste0('https://finance.yahoo.com/calendar/earnings/?symbol=',ticker)
  # read page
  pg <- read_html(URL)
  # look for table
  tbl <- pg %>% html_table() %>% .[[1]]
  # fix date
  tbl$`Earnings Date` <- as.Date(tbl$`Earnings Date`,format="%b %d, %Y, %OS",tz = "America/New_York")
  # limit future releases
  tbl <- subset(tbl, tbl$`Earnings Date` <= as.Date(before))
  # remove duplicate dates
  tbl <- tbl[!duplicated(tbl$`Earnings Date`),]
  # return table
  tbl
}
# fetch earnings
eps_tbl = getEPS(ticker=sym, before = "2024-02-10")
# print eps table
print(eps_tbl)
```

## Get Option Expiry Dates

Get nearest Friday immediately after earnings. Here we will pass the dates & get the nearest Friday following Earnings Date(s)
```{r getExpDates, echo=FALSE}
# extract unique earnings dates
DATES = unique(eps_tbl$`Earnings Date`)
# for each date extract the following Friday
exp_dates = do.call(c, lapply(as.list(DATES), function(x){
  # pass in date and create sequence
  seq_dates = seq.Date(from=x, by="1 day",length.out = 14)
  # trading dates only
  seq_dates = seq_dates[isBusinessDay(calendar = "UnitedStates/NYSE",dates = seq_dates)]
  # find next Friday
  as.Date(seq_dates[which(weekdays(seq_dates) == "Friday")[1]])
}))
# print expiration dates
exp_dates
```

## Get Option Chains

We will get options data from database expirying on the dates from the above dates. Use 20 days prior to expiration.
```{r getOPS, echo=FALSE}
# OPS <- lapply(as.list(exp_dates), function(exp){
#   # fetch options
#   ops <- getOpSymbolsByTickerFromTo(ticker = sym, from = (as.Date(exp) - days(20)), to =  as.Date(exp))
#   # subset to option chain expirying on "exp"
#   ops <- subset(ops, as.Date(ops$expiry) == as.Date(exp))
#   # subset desired columns only
#   ops <- ops[,c("iv", "expiry", "flag", "strike", "stkClose", "Date", "days2Exp", "Mid")]
#   # select OTM only
#   ops$stk2strike <- as.numeric(ops$strike) - as.numeric(ops$stkClose)
#   calls <- subset(ops, ops$flag == "C" & ops$stk2strike > 0) # OTM calls will be positive
#   puts  <- subset(ops, ops$flag == "P" & ops$stk2strike < 0) # OTM puts will be negative
#   ops <- rbind(calls,puts)
#   # return options
#   ops
# })
# # row bind results and return as data frame
# ops <- as.data.frame(do.call(rbind,OPS))
# read in options to save time
ops <- readRDS("pltr_ops.rds")
```


## Get Implied Vols

In this block, we will extract the implied volatility by DTE & calculate the percentage change in IVs
```{r getIVS, echo=FALSE}
# get DTEs > 0
ops <- subset(ops,ops$days2Exp >0)
# summarise data 
ivs = ops %>% group_by(flag, expiry, days2Exp) %>% reframe(avg_iv = mean(iv))
# for each expiry find the % change in IV by DTE
ivs = do.call(rbind,lapply(as.list(unique(ivs$expiry)), function(x){
  # subset table by expiration
  tmp = subset(ivs, ivs$expiry == x)
  # split by calls/puts
  calls = subset(tmp,tmp$flag == "C")
  puts = subset(tmp,tmp$flag == "P")
  # re-order by decreasing DTE
  calls = calls[order(calls$days2Exp, decreasing = T),]
  puts = puts[order(puts$days2Exp, decreasing = T),]
  # find % difference for each day
  calls$pct_ch =ROC(calls$avg_iv,type = "discrete")
  puts$pct_ch = ROC(puts$avg_iv,type = "discrete")
  # return combined table
  na.omit(rbind(calls,puts))
})) %>% as.data.frame()
# multiply iv x 100
ivs$pct_ch = ivs$pct_ch*100
```


## Plot Changes

Plot the changes in IV by DTE
```{r plotIVs, echo=FALSE}
# split by calls/puts
ivs_c = subset(ivs, ivs$flag == "C")
ivs_p = subset(ivs, ivs$flag == "P")

# calls 
ivs_c %>% 
  hchart(
    'line', hcaes(x = 'days2Exp', y = 'pct_ch',group='expiry')
  ) %>%
  hc_xAxis(reversed= TRUE) %>%
  hc_title(text=paste0("Call - IV Changes by DTE"), align="center") %>% 
  hc_tooltip(pointFormat = '{point.y: .3f}%')
# puts
ivs_p %>% 
  hchart(
    'line', hcaes(x = 'days2Exp', y = 'pct_ch',group='expiry')
  ) %>%
  hc_xAxis(reversed= TRUE) %>%
  hc_title(text=paste0("Put - IV Changes by DTE"), align="center") %>% 
  hc_tooltip(pointFormat = '{point.y: .3f}%')
```