---
title: "What is working right now?"
output: html_document
date: "2024-02-09"
---
We attempt to analyze strategy types to see what has been outperforming the market. 
```{r setup, include=FALSE}
require("quantmod");require("PerformanceAnalytics");require("dplyr")
```

## List of Strategies

1. Market Neutral    - `$BTAL` - AGF U.S. Market Neutral Anti-Beta Fund
2. Min Variance      - `$USMV` - iShares MSCI USA Min Vol Factor ETF
3. Momentum          - `$MTUM` - iShares MSCI USA Momentum Factor ETF
4. Income Generation - `$SCHD` - Schwab US Dividend Equity ETF
5. Growth            - `$VUG`  - Vanguard Growth ETF
6. Value             - `$VTV`  - Vanguard Value ETF
7. Merger Arb        - `$MNA`  - IQ Merger Arbitrage ETF
8. Risk Parity       - `$RPAR` - RPAR Risk Parity ETF
9. Event Driven      - `$EVNT` - AltShares Event-Driven ETF
10.Cash              - `$ULST` - SPDR SSgA Ultra Short Term Bond ETF

```{r , echo=FALSE}
# list etfs
etfs <- c("BTAL","USMV","MTUM","SCHD","VUG","VTV","MNA","RPAR","EVNT","ULST")
# assign new env
e <- new.env()
# get data
getSymbols(etfs, from="1990-01-01",env = e)
# combine adjusted closes
ALL <- do.call(merge, eapply(e,Ad))
# format column names
colnames(ALL) <- gsub(".Adjusted","",names(ALL))
# start data Q3 2021 - 10/01/2021
ALL <- ALL["20211001::"]
# calculate returns
RETS  <- do.call(merge,lapply(as.list(1:ncol(ALL)), function(i) monthlyReturn(x=ALL[,i])))
# add column names
colnames(RETS)<- names(ALL)
# calculate monthly SHARPE
SHARPE  <- do.call(merge,lapply(as.list(1:ncol(ALL)), function(i) apply.monthly(x = ROC(ALL[,i]), FUN = function(x){mean(x, na.rm=TRUE)/sd(x,na.rm = T)})))
colnames(SHARPE)<- names(SHARPE)
```

## Cumulative Returns
Returns for all strats.
```{r , echo=FALSE}
# plot performance
charts.PerformanceSummary(RETS, col=rich10equal, cex.legend= 0.55,main = "Cumumlative Returns")
```

## Ranking System
We will rank each ETF by Sharpe each period
```{r , echo=FALSE}
#'@param topN = number of ETFs to return for the portfolio

getStrat = function(topN){
  
  # Find the next period return for the highest Sharpe THIS period
  do.call(rbind,lapply(as.list(1:(nrow(SHARPE)-1)), function(ROW){
    # subsest row/current period
    current_row = SHARPE[ROW,]  
    next_ret = data.frame(Date=as.character(index(SHARPE[ROW+1,])))
    etf_names = c()                    
    # select the returns for each stock
    for(i in 1:topN){
      # which is the highest sharpe this period
      BEST <- which.max(current_row)
      etf_name <- names(SHARPE[,BEST])
      this_ret <- RETS[(ROW+1),etf_name]
      # add to data frame
      next_ret = cbind(next_ret, round(as.numeric(this_ret),5))
      colnames(next_ret)[1+i] <- paste0("etf_",i)
      # add ETF name
      etf_names = c(etf_names,etf_name)
      # remove BEST to grab the next highest
      current_row <- current_row[,-BEST]
    }
    cbind(next_ret, assets = paste(etf_names,collapse = "-"))
  }))
  
}

# Portfolio return - we will assume equal weight
#'@param DF = data.frame returned from previous function
portRet = function(DF){
  # remove last column
  df = DF[,-ncol(DF)]
  # convert to XTS
  XTS = xts(df[,2:ncol(df)], order.by = as.Date(DF$Date))
  # equal-weight
  XTS = reclass(rowMeans(XTS), match.to = XTS)
  colnames(XTS) <- "portfolio"
  # return XTS
  XTS
}

```

# Generate Returns

```{r , echo=FALSE}
# get strategy returns for topN ETFS
DF = getStrat(topN = 5)
# convert to XTS
XTS = portRet(DF=DF)
# plot returns
charts.PerformanceSummary(XTS, main="Portfolio Performance")
```
